AA Distributed Software Development Methodology

### 2013-02-18 paper.tex
5th par improvd

In this paper we propose the AA methodology and an associated software system
for coordinating distributed team work, tackling the disadvantages
of GSD. Team members take on an egalitarian role, and stay
voluntarily \textit{logged} in the system for part of their time
(e.g.\ 2 hours per day), during which they log a periodical short text
sentence --- similar to a ``tweet'' in this Twitter era --- as the
status of their activity using an easy to use command. These
``microblog sentences'' are publicly aggregated and validated by other
team members. Through AA, we have a methodology and an associated
system to validate and enable the activities of a distributed software
team. It implicitly legitimizes financial support for the expansion of
the activity of the developer team. The AA methodology is specially
useful for coordinating distributed and decentralized team work,
providing effective means to asynchronously update different team
members without the need for synchronous unproductive meetings.

>>>>

In this paper we propose the AA methodology and an associated software system
for coordinating distributed team work, tackling the disadvantages
of GSD. Team members take on an egalitarian role, and stay
voluntarily \textit{logged} in the system for part of their time
(e.g.\ 2 hours per day), during which they log a periodical short text
sentence --- similar to a ``tweet'' from Twitter --- as the
status of their activity. Logging is carried out using an easy a series of
available UI's: unix shell
commands, native GUI or web page, conventional social network posts, or chat messages to a log bot
listening to IRC, GTalk, G+, and others.  These ``microblog sentences'' are publicly aggregated and validated by other
team members. Through AA, we have a methodology and an associated system to help
implement and validate the activities of a distributed software team. It implicitly
legitimizes financial support for the expansion of the activity of the developer
team. The AA methodology is specially useful for coordinating distributed and
decentralized team work, providing effective means to asynchronously update
different team members without the need for synchronous unproductive meetings.
